%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% Customised by : Ankush Kapoor
% Github repo : https://github.com/ankushhKapoor/resume
% Hosted link : https://resume-ankushhkapoor.vercel.app
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% Optional: you can uncomment and experiment with fonts here

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ankush Kapoor} \\ \vspace{1pt}
    \small +91 8108405154 $|$  \href{https://ankushhkapoor.vercel.app}{\underline{ankushhkapoor.vercel.app}} $|$
    \href{mailto:work.ankushkapoor1626@gmail.com}{\underline{work.ankushkapoor1626@gmail.com}} \\
    \href{https://github.com/ankushhKapoor}{\underline{github.com/ankushhKapoor}} $|$
    \href{https://linkedin.com/in/ankushhKapoor}{\underline{linkedin.com/in/ankushhKapoor}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vidyalankar Institute of Technology}{\textbf{Mumbai, India}}
      {Bachelor of Technology in Computer Engineering}{Sept 2024 -- Present}
    \resumeSubSubheading
      {First Year - CGPA: \textbf{10.0}}{Second Year, currently ongoing}

    \resumeSubheading
      {Seth Hirachand Mutha School (CBSE Board)}{\textbf{Kalyan, India}}
      {Class XII - \textbf{86\%}}{2024}
    \resumeSubSubheading
      {Class X - \textbf{91\%}}{2022}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Open World Holidays Framework (Open Source Contributor)}{Jan 2025 -- June 2025}
      {Python Framework}{Remote — \href{https://github.com/vacanza/holidays/pulls/ankushhKapoor}{\underline{PRs}}}
      \resumeItemListStart
        \resumeItem{Ranked \textbf{7th out of 2300+ contributors} nationally in Google Winter of Code (WoC) 2024.}
        \resumeItem{Added public holidays for \textbf{India}, \textbf{Nepal}, and \textbf{Mongolia}, covering fixed-date, variable-date, and lunar calendar-based rules.}
        \resumeItem{Implemented \textbf{Hindi} and \textbf{Mongolian} translations to improve localization and accessibility.}
        \resumeItem{Wrote and maintained comprehensive \textbf{unit tests} to validate dynamic holiday calculations.}
        \resumeItem{Contributed to a large-scale \textbf{Python-based database} and participated in detailed code reviews.}
        \resumeItem{Technologies: \textbf{Python}, \textbf{Git}, \textbf{GitHub}, \textbf{Data Processing}, \textbf{Open Source Collaboration}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{KapoorVM (Custom Virtual Machine in C)} $|$ \emph{C, Linux, GCC, Git}}{\href{https://github.com/ankushhKapoor/KapoorVM-16bit}{\underline{GitHub}}}
      \resumeItemListStart
        \resumeItem{Built a 16-bit virtual CPU with a custom instruction set and 65 KB of virtual memory.}
        \resumeItem{Implemented basic opcodes to move immediate values into registers and run a test program.}
        \resumeItem{Designed modular VM components for clean separation of CPU, memory, and instruction handling.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Alloc (Custom Memory Allocator in C)} $|$ \emph{C, Linux, NASM, GCC}}{\href{https://github.com/ankushhKapoor/alloc}{\underline{GitHub}}}
      \resumeItemListStart
        \resumeItem{Created a 32-bit allocator mimicking \texttt{malloc()} and \texttt{free()} over a 1 GB virtual heap.}
        \resumeItem{Implemented \texttt{alloc(bytes)} to allocate memory in words by taking size in bytes as input.}
        \resumeItem{Added \texttt{destroy()} for secure deallocation with memory zeroing to prevent data leakage.}
        \resumeItem{Built packed headers, manual tracking, macros for KB/MB/GB allocation, and a \texttt{show()} debugger.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{CodeNexus (Custom Code Editor in Python)} $|$ \emph{Python, PyQt5, QScintilla, Jedi}}{\href{https://github.com/ankushhKapoor/CodeNexus-Custom-Python-Editor-IDE}{\underline{GitHub}}}
      \resumeItemListStart
        \resumeItem{Developed a tab-based code editor with syntax highlighting, file explorer, and autocomplete.}
        \resumeItem{Implemented a threaded \textbf{AutoCompleter} using \textbf{jedi} and a custom \textbf{QsciLexer}.}
        \resumeItem{Enabled one-click code execution via \textbf{subprocess} in CMD.}
        \resumeItem{Integrated file actions with \textbf{QTreeView} and added keyboard shortcuts.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Email Unsubscriber (Inbox Automation Tool)} $|$ \emph{Python, IMAP, SMTP, BeautifulSoup, requests}}{\href{https://github.com/ankushhKapoor/Python-Email-Auto-Unsubscriber}{\underline{GitHub}}}
      \resumeItemListStart
        \resumeItem{Automated email unsubscription by scanning Gmail inbox via IMAP and locating unsubscribe links.}
        \resumeItem{Parsed links using \textbf{BeautifulSoup} and text-matching logic.}
        \resumeItem{Visited each link via \textbf{requests} and logged success/failure locally.}
        \resumeItem{Used \texttt{dotenv} to securely manage credentials.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C, Java, MySQL, HTML, CSS} \\
     \textbf{Tools \& Environments}{: Git, GitHub, Linux (Ubuntu/WSL, VirtualBox), VS Code, Neovim, tmux, IntelliJ IDEA} \\
     \textbf{Frameworks}{: Tailwind CSS}
    }}
 \end{itemize}

\end{document}
